### 2012-07-10 1.tex
Feverish writing on chapters 2-4
Writing on chapters 2, 4

\section{A brief history of MSCs} \input{1.1}
\section{The null hypothesis} \input{1.2}
\section{Outline of Part I} \input{1.3}

>>>>

\section{A brief history of MSCs}

A more expressive approach to problems of this type, making no reference to \citeauthor{Bloomfield1930}'s study, was published only two years later. \citet{Jakobson1932}, then a member of the Prague circle, attributes a number of phonological properties of the Russian imperative to particular types of juncture, a precursor of morphological levels \citep[e.g.,][]{Siegel1974} in Lexical Phonology. Nearly all Russian infinitives are marked with a final theme vowel and /-t\pal{}/. In reflexives, this is followed by a suffix realized as [s\pal{}ə], which triggers a general process of regressive voicing assimilation. In the reflexive infinitive, the palatalization of infinitive /-t\pal/ is lost, but palatalization of a stem-final consonant is preserved in the reflexive imperative, even when the root-final consonant is /t\pal/, as in (\ref{rusreflex}c).\footnote{Thanks to Lev Blumenfeld for discussion of this data.}

\begin{example}[Russian reflexives] \label{rusreflex}
\begin{tabular}{l l l l}   & \emph{infinitive} & \emph{imperative} \\
a. & [slav\pal{}itsə]  & [slaf\pal{}s\pal{}ə]  & `be glorious'   \\
   & [upram\pal{}itsə] & [upram\pal{}s\pal{}ə] & `be stubborn'   \\
b. & [kras\pal{}itsə]  & [kras\pal{}s\pal{}ə]  & `put on makeup' \\
   & [ʒar\pal{}itsə]   & [ʒar\pal{}{}s\pal{}ə] & `roast'         \\
c. & [zəbytsə]         & [zəbut\pal{}s\pal{}ə] & `forget'        \\
\end{tabular}
\end{example}

\noindent \citeauthor{Jakobson1932} proposes that the preservation of palatalization in /\ldots{}t\pal{}-s\ldots{}/ is a special property of the imperative. Both (\ref{rusreflex}c) forms contain a /t\pal-s/ juncture, though palatalization is only preserved in the imperative. \citeauthor{Jakobson1932} proposes that the phonology treats them differently: the imperative does not undergo loss of palatalization.
%A few years later, \citet{Trnka1936} makes the connection between \citeauthor{Jakobson1932}'s hypothesis and phonotactic gener

nstraints.

\subsection{Static phonotactics and the lexicon}

If juncture may give rise to sound sequences not found in what are now called \emph{non-derived environments}, it follows that the morph represents a privileged domain for phonotactic generalizations. \citet{SPR,Halle1962} and \citet{Chomsky1965,SPE} posit a system of a system of \emph{morpheme structure constraints}---more precisely, \emph{sequence structure constraints} \citep{Stanley1967}---used to fill out redundant specifications in underlying forms, and to account for speakers' knowledge of possible words.

This too can be traced to late structuralist thinkers, for example Kenneth Pike. \citet{Pike1947b} discusses a number of constraints on vowel sequences in Mixteco. It is apparent that \citeauthor{Pike1947b} does not expect these constraints to hold across junctures when comparing these constraints to his analysis of a Mixteco text published a few years earlier \citep{Pike1944}.\footnote{The junctures posited by \citet{Pike1944} are indicated with a dash, but this is not intended to imply that juncture is necessarily a phonetic event \citep[cf.][55f.]{Scheer2011}.}

\begin{example}[Mixteco MSCs and complex words \citep{Pike1944,Pike1947b}]\begin{tabular}{l l@{} l l l}
a. & * & {C}a{C}e & [ká-\textsuperscript{n}dee]     & `kept inside'   \\
b. & * & {C}ə{C}e & [nì-k\`əbə]                     & `and entered'   \\
c. & * & {C}e{C}i & [te-ní-ke\textsuperscript{n}da] & `was walking    \\
d. & * & {C}i{C}e & [te-nì-kee]                     & `and went away' \\
\end{tabular}
\end{example}

\noindent \citet[][166]{Pike1947b} writes that junctures are ``marked'' by the presence of sequences which cannot be found morph-internal, an idea further developed by \citet{Harris1955} as a discovery procedure for morphs (see also \citet{H

Much later, \citet{McCarthy1988} and \citet{Mester1988} assume that these lexical constraints do not have to be exceptionless to be psychologically real; any statistically reliable pattern is potential evidence for the organization of feature systems, structural descriptions, and the like. Though these two studies have been widely imitated and in dozens of languages (a near-exhaustive list can be found in \citealp[?]{Brown2010} ), \citeauthor{McCarthy1988} and \citeauthor{Mester1988} never present a linking hypothesis for the connection between static lexical patterns and phonology. What follows is a sketch of such an argument. First, lexical patterns are delimited in the units of phonology \citep[9]{Berkley2000}: phonemes, syllables, and the like. The acquisition heuristic known as \emph{Stampean occultation} \citep[54]{OT} imposes phonological alternations root-internally, so that statistically reliable lexical patterns can plausibly be traced to the phonology of the recent past. For instance, virtually all obstruent-obstruent sequences in the English lexicon consist either of two voiced, or two unvoiced, consonants (see \S\ref{ova} below). This corresponds to the fact that English has---and has had for at least a millenium---a process of \textsc{Obstruent Voice Assimilation}. Unfortunately, few of these later studies distinguish between phonotactics derived by alternations and those which are have no analogue in the synchronic phonology and thus are ``static''. This chapter is a first attempt to fill this lacuna.

\subsubsection{Biuniqueness and neutralization}

joos
harris
chomsky

\subsection{Early generativism}

\subsubsection{\citealt{Stanley1967}}

inventory constraints
sequence constraints

\subsubsection{Surface constraints and occultation}

shibatani
stampe
dell

\emph{A}[mt] `office', \emph{Anbau} `cultivation'
\emph{ei}[n.g]\emph{reifen} `to intervene',

\subsubsection{The duplication problem}

\citeauthor{Anderson1974} sees the duplication of \textsc{Backness Harmony} as both sequence structure constraint and phonological rule as a foregone conclusion
.The tendency of sequence structure constraints to duplicate phonological rules was noted by \citet[][401f.]{Stanley1967} and in \emph{SPE} (p.~382) in the discussion of morpheme structure constraints, and is labeled ``the duplication problem'' by \citet[][?]{Kenstowicz1977}.

inventory problems 
dell, chung, but also problems

conspiracies

\subsection{Autosegmentalism}

also ``supersegmentalism''

The proposals during this period are very diverse.

\subsubsection{Syllable structure}

hooper
noske

\subsubsection{Morph features}

Leben
Kaye

\subsubsection{The Obligatory Contour Principle}

\subsection{Classic Optimality Theory}

%(page numbers here are taken from the published version)

\subsubsection{Richness of the Base}

some quotes from OT doc
\citet{PE}
\citet{Bye2001}

\subsubsection{Freedom of Analysis}

\citet{Smolensky1996}
\citet{PE}

\subsubsection{Undominated constraints}

% complaints about maceahern, gallagher
% bit on loanword adaptation

\subsection{Recent developments}

\subsubsection{Language acquisition}
% jusczyk forever
% white et al.
% early word learning
% syllables

\subsubsection{Psycholinguistic tasks in adults}

% wordlikeness
% spotting
% error correction, etc.

\subsubsection{Non-native word adaptation}

% perceptual factors

\section{The null hypothesis}

\subsection{The empirical proposal}

\subsection{The acquisition principle}

\subsection{Falsifiability}

%\subsection{Universal constraints?}    \input{1.2.4}

\section{Outline of the dissertation}

%Chapter 2
%Chapter 3
%Chapter 4
